Finding ARG1 of Partitive Nouns in NomBank with DistilBERT

### 2022-05-04 src/paper.tex
Update

>>>>

\subsection{Partitive Dataset}

Apart from the original \% task, we also experimented the token classification of DistilBERT on the combined dataset of \% and partitive datasets of NomBank. Different from the \% dataset, there's not only ARG1 but also ARG0, ARG2... and more role labels in the partitive dataset. In order to adopt the same pipelines, we preprocessed the partitive dataset into the same format as the \% dataset and combine them together into a larger dataset. The larger dataset is also split into training, dev and test set. The training set has 12991 sentences or 380247 words, the dev set has 426 sentences or 12671 words, and the test set has 746 sentences or 21536 words.
